---
title: "Visualize Data"
author: "Michael Torrisi"
date: today
format: gfm
self-contained: true
editor: source
execute: 
  echo: true
  error: true
code-fold: true
toc: true
theme: default
fontcolor: black
linkcolor: blue
monobackgroundcolor: rgb(199, 221, 235)
backgroundcolor: rgb(200, 200, 200)
---


```{r}
#| label: setup
#| include: false
library(tidyverse)
```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: Load Dataset
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: First Visualization: Scatterplot
# Creates scatterplot with in-built mpg dataset
ggplot(mpg) + 
  geom_point(aes(x = displ,
                 y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: Second Visualization: Boxplot
# Creates boxplot with in-built mpg dataset
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class,
                           y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: Third Visualization: Histogram
# Creates histogram with in-built mpg dataset
ggplot(data = mpg) +
  geom_histogram(aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: Fourth Visualization: Histogram with Binwidth
# Creates histogram with in-built mpg dataset, and controls binwidth.
ggplot(data = mpg) +
  geom_histogram(aes(x = hwy), binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}

```

## Quiz

What will this code do?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy)) 
  ggsave("example.jpg")
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```